Progress with the NOSAMS<br>Hybrid Gas Ion Source

### 2021-05-03 doc/SNEAP2021/SNEAP2021_HGIS_presentation/SNEAP2021_HGIS_presentation.Rmd
Minor edits.

- Skip a time-consuming reduction to graphite
- Rapid iteration for science/development
- Eliminate blank associated with graphitization

@@

- Ultimate precision is lower
- Lower currents/counts (time to precision)
- Variability in blank (current dependent)
- Variability in sample performance
]

@@

### Data summary
* mean difference: `r format(mean(carb_data$fmbc_diff), digits = 1)`
* sd of difference: `r format(sd(carb_data$fmbc_diff), digits = 2)`

@@

###Goals:
* Finish characterization of the method
* Compare to graphite with test samples
* Improve accuracy
* Better understand method blank
* Reduce sample size
* Automate data acquisition and reduction

>>>>

- Skip a time-consuming reduction to graphite
- Rapid iteration for science and development
- Eliminate blank associated with graphitization

@@

- Ultimate precision is lower
- Lower currents/counts (time to precision)
- Variable blank (current dependent)
- Reproducible sample performance
]

@@

### Data summary
* Mean difference: `r format(mean(carb_data$fmbc_diff), digits = 1)`
* Standard deviation of difference: `r format(sd(carb_data$fmbc_diff), digits = 2)`

@@

### Goals:
* Finish characterization of the method
* Compare to graphite with test samples
* Improve accuracy
* Better understand method blank
* Reduce sample size
* Automate data acquisition and reduction
